\documentclass[11pt]{article}

\usepackage[margin=1.5cm]{geometry}

\begin{document}

\begin{center}

{\bf Presentation Schedule for extra credit - Up to 3 students per day}

\vspace{1cm}

\end{center}




DAY:  Thu, Oct. 17

\begin{itemize}

\item[1.]

\item[2.]

\item[3.]

\end{itemize}


DAY:  Tue, Oct. 22

\begin{itemize}

\item[1.]

\item[2.]

\item[3.]

\end{itemize}


DAY:  Thu, Oct. 24

\begin{itemize}

\item[1.]

\item[2.]

\item[3.]

\end{itemize}


DAY:  Tue, Oct. 29

\begin{itemize}

\item[1.] Jangheum Park: “Survival rate in Mars”

\item[2.] Sanha Jang: ``Blue Super Moon''
  
\item[3.]

\end{itemize}


DAY:  Thu, Oct. 31

\begin{itemize}

\item[1.] 

\item[2.]

\item[3.] 

\end{itemize}


DAY:  Thu, Nov.7

\begin{itemize}

\item[1.] Maisha Mahzabin: ``Strange Exoplanets'' 

\item[2.] Lenin Nolasco: ``Weird Moons''

\item[3.]

\end{itemize}

DAY:  Tue, Nov.12

\begin{itemize}

\item[1.] Andrew Kim

\item[2.] Justin Kim

\item[3.]

\end{itemize}

DAY:  Thu, Nov.14

\begin{itemize}

\item[1.] Vanessa Brill: ``Hot Jupiters''

\item[2.] Nicholas Esteves: ``Brown Dwarves'' 

\item[3.]

\end{itemize}



DAY:  Tue, Nov. 19

\begin{itemize}

\item[1.] Jiwon Lee 

\item[2.] Jaesuk Song

\item[3.] Zoe Lucas

\end{itemize}


DAY:  Thu, Nov. 21

\begin{itemize}

\item[1.] Hayeon Jin: ``Planet 9''

\item[2.] Emma Felt: ``Europa's Clipper''

\item[3.] Brett Kitograd: ``Weather patterns on other planets''

\end{itemize}


DAY:  Tue, Nov. 26

\begin{itemize}

\item[1.]  Shengze Wang

\item[2.] Sheina Peralta

\item[3.] Rose Hoffren: ``Planet formation'' 

\end{itemize}


DAY:  Tue, Dec.3

\begin{itemize}

\item[1.]  Kimberly Horvat: ``Transit Method for Detection'' 

\item[2.] Cyrus Villanueva

\item[3.] Siyuan Xia

\item[4.] Daniel Derienzis: ``James Webb Observations of planets''

\item[5.] Yelin Cheon: ``Lunar exploration''  
  
  

\end{itemize}


%DAY:   

%\begin{itemize}

%\item[1.]

%\item[2.]

%\item[3.]

%\end{itemize}





\end{document}


